Modeling the competing effects of the immune system and EMT on epithelial cancers

### 2019-11-27 Paper/CleanPaper.tex
Finished updating all figures with new runs
Updated fig2 and a little wording

\begin{framed}
    {\bf Quick Guide to Equations and Assumptions}
\newline
An in situ tumor relies on mutations to alter cellular signaling pathways that will ultimately allow the tumor to become invasive. The immune system

    At the same time, the immune system is recognizing and adapting to the resulting neoantigens to suppress the tumor.
    All of this occurs within an environment that is often under the influence of inflammatory signals that can vary over time.

@@

    The second term is a hill function similar to the de Pillis-Radunskaya law.

@@

    Here, we choose TGF-$\beta$ as a master regulator of EMT and connect the TGF-$\beta$ level in the tumor microenvironment (TME) with the propensity of tumor cells to undergo EMT.

@@

\begin{table}[H]
\begin{tabular}{|p{\textwidth}|}
\hline
%%%
\begin{itemize}
\item TGF-$\beta$ is well-mixed within the TME
\item All cells are on the same ``clock'', i.e. they all decide at the same time what to do next
\item During a given cell cycle, exactly one event can happen to any one cell: proliferation, apoptosis, immune clearance, or rest
\item All tumor cells (mutated and non-mutated) are equally likely to encounter immune cells
\item Other spatial effects are ignored by the model, e.g. angiogenesis, hypoxia, invasive front, and chemotaxis
\item The initial cells are mutated, but are not able to form an aggressive cancer without further mutations
\end{itemize}
\\
\hline
\end{tabular}
\caption{Basic assumptions of the model}
\label{table:model_assumptions}
\end{table}

@@

\begin{figure}
\center
{\includegraphics[width=0.85\textwidth]{Figure2/Figure2.jpg}}
\caption{Sensitivity analysis of model parameters, determined via the global Morris one-step-at-a-time method. $\mu^*$ denotes the average absolute change in Time to Cancer when the parameter is varied.}
\label{fig:MOAT}
\end{figure}

@@

\begin{figure}
\center
{\includegraphics[width=0.5\textwidth]{Figure5/MIEvsMGA_bigcbar.jpg}}
\caption{Summary of the contrasting effects of MIE and MGA on the Time to Cancer.
}
\label{fig:MIEvsMGA}
\end{figure}

>>>>

\begin{framed}
    {\bf Quick Guide to Equations and Assumptions}
An in situ tumor relies on mutations to alter cellular signaling pathways that will ultimately allow the tumor to become invasive. The immune system responds to the tumor upon recognition of the neoantigens and infiltrates the tumor microenvironment (TME). This environment is under the influence of inflammatory signals that vary over time.
%
%    At the same time, the immune system is recognizing and adapting to the resulting neoantigens to suppress the tumor.
%    All of this occurs within an environment that is often under the influence of inflammatory signals that can vary over time.

@@

    The second term is a hill function similar to the dePillis-Radunskaya law and it assumes that the immune cells are well-mixed within the TME.

@@

    Here, we choose TGF-$\beta$ as a master regulator of EMT and connect the well-mixed TGF-$\beta$ level in the TME with the propensity of tumor cells to undergo EMT.

@@

%\begin{table}[H]
%\begin{tabular}{|p{\textwidth}|}
%\hline
%%%%
%\begin{itemize}
%\item TGF-$\beta$ is well-mixed within the TME
%\item All cells are on the same ``clock'', i.e. they all decide at the same time what to do next
%\item During a given cell cycle, exactly one event can happen to any one cell: proliferation, apoptosis, immune clearance, or rest
%\item All tumor cells (mutated and non-mutated) are equally likely to encounter immune cells
%\item Other spatial effects are ignored by the model, e.g. angiogenesis, hypoxia, invasive front, and chemotaxis
%\item The initial cells are mutated, but are not able to form an aggressive cancer without further mutations
%\end{itemize}
%\\
%\hline
%\end{tabular}
%\caption{Basic assumptions of the model}
%\label{table:model_assumptions}
%\end{table}

@@

\begin{figure}
\center
{\includegraphics[width=0.85\textwidth]{Figure2/MOAT.jpg}}
\caption{Sensitivity analysis of model parameters, determined via the global Morris one-step-at-a-time method. $\mu^*$ denotes the average absolute change in Time to Cancer when the parameter is varied.}
\label{fig:MOAT}
\end{figure}

@@

\begin{figure}
\center
{\includegraphics[width=0.5\textwidth]{Figure5/heatmap2.jpg}}
\caption{Summary of the contrasting effects of MIE and MGA on the Time to Cancer.
}
\label{fig:MIEvsMGA}
\end{figure}
